\documentclass{amsart}
\input{assets/preamble.tex}
\begin{document}

% =================================================
% TITLE & AUTHORS
% =================================================
\title{%
        The Borsuk-Ulam theorm in real-cohesive homotopy
        type theory}   
\author{%
        Daniel Cicala \and Chandrika Sadanand \and Michael
        Shulman \and Amelia Tebbe}
\begin{abstract}
        Borsuk-Ulam!
\end{abstract}
\maketitle

% =================================================
% SECTION: COMMENTARY
% =================================================
\section*{Writing Notes}
\label{sec:writing_notes}

Writing assignments:
\begin{itemize}
\item Amelia---section 5
\item Chandrika---section 4
\item Daniel---sections 2 and 3
\end{itemize}

Formalizing the cohomology proofs will be determined later.

% =================================================
% SECTION: INTRODUCTION
% =================================================
\section{Introduction}
\label{sec:intro}

% =================================================
% SECTION: OVERVIEW OF REAL COHESIVE HOTT
% =================================================
\section{Overview of real-cohesive homotopy type theory}
\label{sec:rc-hott}

OUTLINE:
\begin{itemize}
\item
  HoTT as foundations
\item
  Interpreting AlgTop theorems in HoTT is obstructed by
  discontinuous functions
\item
  Relating continuous and discontinuous with flat and
  sharp, which are borrowed from cohesive topoi
\item
  Formalizing flat and sharp in HoTT + axioms needed,
  e.g. Rflat
\item
  Connecting sets used in AlgTop with HITs used in HoTT
  via shape
\end{itemize}

Homotopy type theory (HoTT) is an expression of a style of
mathematics that expands the notion of ``identity'' to
include logical identity, homotopy equivalence, and path
connectedness.  Experts call this style \emph{Univalence
  foundations}. And as foundations, there is an ambitious
program to encode all of mathematics in homotopy type
theory. There is a growing community working to realize
these ambitions and this paper belongs to this group.

Our present goal is to bring the classical theory of
algebraic topology into the fray, and in particular the
Borsuk-Ulam theorem.  However, the HoTT approach to
algebraic topology comes with an immediate challenge: the
presence of so many fixed point theorems where, in the
course of a proof, the fixed point must be specified
precisely, not only up to homotopy.  What is the problem
with this?  It is that homotopy type theory only works up to
homotopy. Compare, for instance, the topological circle
$$ \SS^1 \bydef \left\{ (x,y) \in \RR^2 | x^2 + y^2 = 1
\right\} $$ with the homotopy type theoretical circle
defined by a pair of constructors $ \type{base} $ and
$ \type{loop} \tin \type{base} = \type{base}$. One has
infinitely many points that can be described exactly and the
other has a single point. Brouwer's Fixed Point Theorem
illustrates this problem nicely. We provide its statement
and proof here for reference.

\begin{theorem}
  Let $ \DD^2 $ denote the topological disk $ \left\{ (x,y)
      \in \RR^2 | x^2 + y^2 \leq 1 \right\} $.  Any
  continuous map $ f \from \DD^2 \to \DD^2 $ has a fixed point.
\end{theorem}

\begin{proof}
  Suppose that $ f $ is continuous but does not have a fixed
  point, hence $ f(x) \neq x $ for all $ x \in \DD^2 $.
  For each $ x \in \DD^2 $, dray a ray from $ f(x) $ to $ x
  $. This ray intersects the circle in a point we denote by
  $ s(x) $. This defines a continuous function $ s \from
  \DD^2 \to \SS^1 $ with the property that $ s(x)=x $ for all $ x $ on
  the boundary of $ \DD^2 $.  That implies that the identity
  on $ \SS^1 $ factors as the inclusion $ \SS^1
  \hookrightarrow \DD^2 $ followed by $ s $.  Appying the
  fundamental group function $ \pi_1 $ to this factorization
  gives that the identity on $ \pi_1 \left( \SS^1 \right) =
  \ZZ $ factors through $ \pi_1 \left( \DD^2 \right) = 1 $
  which is absurd.
\end{proof}

Note how this proof relied on our precise specification of
the point $ s(x) $ on the circle.  This point cannot be
specified precisely in HoTT. Even if we did work with the
only homotopical point on the circle, that is with $ \S^1 $,
there is no way to relate $ \SS^1 $ to $ \S^1 $ inside of
type theory. Semantically speaking, this involves comparing
a topological space with $ \infty $-groupoids. This is done
using the fundamental $ \infty $-groupoid construction.  No
such construction exists in HoTT. This is the problem that
real-cohesive homotopy theory solves. It does so by
proposing to combine two already existing, but previously
unrelated, type semantics: topological and
$ \infty $-groupoidal. With this proposal, there are three
puzzles to be solved.

\begin{enumerate}
\item We need to define a model for a \emph{topological $ \infty
    $-groupoid}.
\item What rules or axioms can we equip HoTT with so that we
  can compare, for example, $ \SS^1 $ to $ \S^1 $.
\item Topology \Amelia{Type theory?} is incompatible with the law of the excluded
  middle, which is required to prove these classic fixed
  point theorems. How can we resolve this?
\end{enumerate}

Shulman's original paper on real-cohesive HoTT
\cite{shul:bfp} discusses the solution to these puzzles in
detail. Presently, we are content to simply say that the
Lawvere's theory of cohesion offers a solution. Of course,
we need to adapt cohesion to homotopy type theory and we
leave the description of this to Shulman, but we do provide
a high-level description of the role that cohesion plays.

A \emph{category of cohesive space} is a pair of categories
equipped with a string of adjunctions
\[
\begin{tikzcd}[row sep = 25pt]
  \cat{Spaces}
    \arrow[d, shift left = 1em, "f_\ast"']
    \arrow[d, shift right = 3em, "f_!"'] \\
  \cat{Sets}
    \arrow[u, shift left = 1em, "f^\ast"]
    \arrow[u, shift right = 3em, "f^!"] 
\end{tikzcd} 
\]
with $ f_! \dashv f^\ast \dashv f_\ast \dashv f^! $ and such
that $ f_! $ preserves finite products.  As Lawvere puts it,
the objects of $ \cat{Sets} $ should be thought of as
\emph{abstract sets} which
\begin{quote}
  ... may by conceived of as a bag of dots which are devoid
  of properties apart from mutual distinctness \cite{lawvere:cohesive}.
\end{quote}
On the other hand, the objects of $ \cat{Spaces} $ should be
thought of as abstract sets together with a sort of
\emph{cohesion} between the ``dots''. For our purposes, we
think of cohesion as a topology though, in reality, this
definition above axiomatizes the various forms that cohesion
may take, each functor playing a different role.  The
$ f_! $ functor tells us which points are ``stuck'' together
through the cohesion by returning a set of connected
components. The $ f^\ast $ functor endows a set with the
discrete topology. The $ f_\ast $ functor forgets the
topology of a space. The $ f^! $ functor endows a set with
the codiscrete topology on a set.  From this string of
adjoints, we get another adjoint string
$ \int \dashv \flat \dashv \sharp $ on $ \cat{Spaces} $
comprised of the \defn{shape operation}
$ \int \bydef f^\ast f_! $, the \defn{flat operation}
$ \flat \bydef f^\ast f_\ast $, and the \defn{sharp operation}
$ \sharp \bydef f^! f_\ast $.

To see how the axiomatic cohesion addresses the above
puzzles, we will speak in the language of sets and
categories instead of type theory. In other words, we
restrict out attention to the semantics of the relevant type
theory.

To solve the first puzzle, constructing a topological
$ \infty $-groupoid, we ask first that $ \cat{Spaces} $ and
$ \cat{Sets} $ are toposes. A cohesive topos is also a
\emph{local and locally connected topos} which can be
constructed using sheaves on a site that satisfy certain
properties. By expanding this construction to the
$ (\infty,1) $-category, we can obtain cohesive
$ (\infty,1) $-toposes using $ \infty $-sheaves on a site as
shown by Schreiber \cite{schreib:diff}.  The objects of a
resulting cohesive $ (\infty,1) $-topos are precisely the
topological groupoids we seek.

The second puzzle involves comparing a space with its
homotopy type.  Again modifying axiomatic cohesion, we
replace the categories $ \cat{Sets} $ and $ \cat{Spaces} $
with the $ (\infty,1) $-categories of $ \cat{Spaces} $ and $
\infty-\cat{Groupoids} $. We also replace the functors with
$ \infty $-functors.  The validity of this rests on work by
Schreiber \cite{schreib:diff}. In this setup, applying $
\shape $ to a space returns the fundamental $ \infty
$-groupoid, an excellent proxy for the homotopy type.  

Axiomatic cohesion also provides a solution to the final
puzzle: the failure of the \emph{continuous} excluded
middle. Given that we are working with topological objects,
we require that excluded middle holds continuously, but in
general it does not. Given a space $ X $ and subspace $ U $,
there is no continuous inverse to the inclusion
$ U + (X \setminus U) \to X $ because, even though the
underlying sets are the same, the topologies are
different. If we can introduce discontinuous functions
$ X \to U + (X \setminus U) $, then we can find a
discontinuous inverse to the inclusion, therefore obtaining
a modified, ``discontinuous'' law of the excluded
middle. Hence, the existence of a law of the excluded middle
in our context hinges on the introduction of such
discontinuous functions. To this end, recall that $ \flat $
retopolozes discretely and $ \sharp $ retopologizes
codiscretely. If $ \hom (X,Y) $ is the space of continuous
functions from $ X $ to $ Y $, then both $ \hom (\flat X,Y)
$ and $ \hom (X,\sharp Y) $ contain the discontinuous, by
which we mean not necessarily continuous, functions from $ X
$ to $ Y $.  

Moving towards syntax means introducing into homotopy type
theory the constructors that mirror the semantics of $ \int $,
$ \flat $, and $ \sharp $. Upon adding these constructors,
we obtain \emph{cohesive homotopy type theory}. The ``real''
part of name comes from an additional axiom included so that
we can capture the topology syntactically using continuous
paths from the reals. This axiom states
\begin{center}
\begin{quotation}
  A crisp type $ \type{A} $ is discrete if and only if the
  function that returns a constant path
  $ \type{A} \to (\RR \to \type{A}) $ is an equivalence.
\end{quotation}
\end{center}
Calling $ \type{A} $ a crisp variable means that we
perform constructions on it without regarding the topology,
such as defining maps $ \flat\type{A} \to \type{Y} $ or $
\type{X}\to\sharp\type{A} $.  When including this axiom
along with the syntactic versions of shape, flat, and sharp,
we get \emph{real-cohesive homotopy type theory}.















% =================================================
% SECTION: TRANLATING BORSUK ULAM TO HOTT
% =================================================
\section{Translating Borsuk-Ulam to homotopy type theory}
\label{sec:bu-to-hott}

OUTLINE:
\begin{itemize}
\item
  \textbf{Subsection 1.} Give statements for BU-classic,
  BU-odd, BU-retract) a la wikipedia. The proof strategy:
  show BU-retract implies BU-odd which is equivalent to
  BU-classic, then prove BU-retract. Give the proof for
  BU-retract.
\item \textbf{Subsection 2.} Translate the classical statement into
  propositions as types. We want to model classical proof as much as
  possible.  Notes on intuitionistic logic: contrapositive holds one
  way, i.e. $p \to q$ entails $-q \to -p$, and the inverse isn't true.
  The rule $p \to -q$ is equivalent to $q \to -p$ in intuitionistic
  logic. Due to this, our proof strategy is BU-retract implies not not
  BU-odd which is equivalent to not not BU-classic. But not not
  BU-classic is sharp BU-classic. Prove BU-retract.
\item
  To close out the section, list the ingredients we need to
  prove BU-retract.
\end{itemize}

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{The classical Borsuk-Ulam Theorem}

In classical algebraic topology, the Borsuk-Ulam theorem is given
as the three equivalent statements listed below. The first of these
statements is taken as the standard presentation.

\begin{statement}\label{BUClassic}
  If $f: \SS^n \rightarrow \RR^n$ is a continuous function, then there
  exists a point $x \in \SS^n$ such that $f(x) = f(-x)$, where $-x$ is
  the antipodal point of $x$.
\end{statement}

\begin{statement}\label{BUOdd}
  Any odd continuous function $g: \SS^n \rightarrow \RR^n$ must have a
  zero.
\end{statement}

\begin{statement}\label{BURetract}
  There is no odd continuous function $h:\SS^n \rightarrow \SS^{n-1}$.
\end{statement}

Of the many approaches to proving Borsuk-Ulam, we share one that
parallels our approach to proving the HoTT version.  That is, show
that each of the three statements are truly equivalent, then prove
Statement \ref{BURetract}. Though the classical version of this
approach is well-documented, we sketch it below.

To see that Statement \ref{BUOdd} implies Statement
\ref{BUClassic} note that given a continuous function $f$, one can
construct a continuous function $g(x) = f(x) - f(-x)$ that is, by
definition, odd. To see the opposite implication, start with a
continuous odd function $g$ which by assumption has some $x \in \SS^n$
such that $g(x)=g(-x)$. Then, since $g$ is odd, $g(-x) = -g(x)$ holds
for this $x$, which implies that $g(x)= -g(x)$, hence $g(x)=0$.

Statement \ref{BUOdd} implies \ref{BURetract}. Indeed, any odd
continuous $h \from \SS^n \to \SS^{n-1} \subseteq \RR^n$ must have a
zero, but $0 \not\in \SS^{n-1}$, so no such $h$ exists.  Conversely,
suppose that an odd continuous $g \from \SS^n \to \RR^n$ has no zero,
then the map $h(x) = g(x) / \vert g(x) \vert$ defines an odd
continuous function $h \from \SS^n \to \SS^{n-1}$. 

Now having the equivalnce of the three statements, proving them
proceeds in three cases: $n=1$, $n=2$, and $n \geq 3$.

For $n=1$, we prove Statement \ref{BUOdd}. Given an odd continuous
$g \from \SS^1 \to \RR^1$ and a chosen $x$, then either $g(x)=0$ in
which case we are done or, without loss of generality, $g(x) > 0$
which means that $g(-x) < 0$.  Apply the intermediate value theorem.

% TODO include n=2 case here

Finally, holding $n \geq 3$, let $h:\SS^n \rightarrow \SS^{n-1}$ be a
continuous odd function. Since $h$ is odd, we can identify antipodal
points and arrive at the induced continuous function
$h':\RRP^n\rightarrow\RRP^{n-1}$. Note that the fundamental groups of
$\RRP^n$ and $\RRP^{n-1}$ are both $\ZZtwo$.  Thus, if the
homomorphism of fundamental groups induced by $h'$ is nontrivial, it
will also be an isomorphism.  Since the fundamental group of $\RRP^n$
is $\ZZtwo$, it has a nontrivial element. Therefore there must exist a
representative loop $\gamma$ in $\RRP^n$ that is essential. The loop
$\gamma$ can then be lifted to $\SS^n$, resulting in a path $p$
between antipodal points in $\SS^n$ (since $\SS^n$ is the universal
cover of $\RRP^n$). Applying the odd map $h$ to this path $p$, we get
a path $h(p)$ between two antipodal points in $\SS^{n-1}$, which then
projects to a loop $h'(\gamma)$ in $\RRP^{n-1}$. If $h'(\gamma)$ was
null homotopic, the null homotopy would lift to $\SS^{n-1}$,
contradicting that $h(p)$ is a path between antipodal points in
$\SS^{n-1}$.
 
Using the Hurewicz homomorphism and universal coefficient theorem, we
get an induced graded ring homomorphism on cohomology with $\ZZtwo$
coefficients,
$h^*:H^*(\RRP^n;\ZZtwo)\leftarrow H^*(\RRP^{n-1};\ZZtwo)$, where
$H^*(\RRP^n;\ZZtwo)\cong \ZZtwo[a]/\langle a^{n+1}\rangle$ and
$H^*(\RRP^{n-1};\ZZtwo)\cong \ZZtwo[b]/\langle b^n\rangle$
(\Amelia{Why was this again?}).  Since
$h':\RRP^n\rightarrow\RRP^{n-1}$ induces an isomorphism on the
fundamental groups, and the Hurewicz homomorphism is an isomorphism at
the $i=1$ level, the induced homomorphism $h^*$ must send $b$ to
$a$. This implies that $b^n$ is sent to $a^n$, which is a
contradiction since $b^n=0$ and $a^n\neq 0$.  Thus, no such map
continuous odd map $h:\SS^n \rightarrow \SS^{n-1}$ can exist.

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Translating the classical Borsuk-Ulam Theorem into HoTT}

We now translate the three classical Borsuk-Ulam statements into their
homotopy theory theoretic versions. This process takes two steps.  The
first step is writing the statements in the language of standard
homotopy type theory. While we do show that these are equivalent to
each other, we do not try to prove them. Indeed, each bound variable
depends continuously on the free variable which is far too strong a
condition. This brings us to the second step of translating from
statements in standard homotopy type theory into real cohesive
homotopy type theory. The equivalence between statements will remain
and we gain the ability to break the bound variables continuous
dependence on the free variable so that we can actually prove that the
statements are true.

Here are the statements in standard homotopy type theory.  Below them,
we show they are equivalent. Do note that $\RR$ refers to the Dedekind
reals and $\SS^1$ is the topological circle
$\{ (x,y) \in \RR^2 \from x^2+y^2=1\}$ and not the higher inductive
circle with a single 0-type and single, non-trivial 1-type, which we
denote by $\S^1$.

\begin{statement}\label{BUClassic-HoTT}
  For any function $f \from \SS^n \to \RR^n$, we have
  $\sum\limits_{x \tin \SS^n} f(x) = f(-x)$.
\end{statement}

\begin{statement}\label{BUOdd-HoTT}
  For any odd continuous function $g: \SS^n \rightarrow \RR^n$, we have
  $\sum\limits_{x : \SS^n} (g(x) = 0)$.
\end{statement}

\begin{statement}\label{BURetract-HoTT}
  For any continuous function $h \from \SS^n \to \SS^{n-1}$, we
  have $\neg \prod\limits_{x : \SS^n} -h(x) = h(-x)$.
\end{statement}

To show these are equivalent is more subtle than the classical case
because we are using intuitionistic logic.  Statements
\ref{BUClassic-HoTT} and \ref{BUOdd-HoTT} are equivalent for the same
reason as in the classical case. The different lies in showing the
equivalence between Statements \ref{BUOdd-HoTT} and
\ref{BURetract-HoTT}.

Let us denote Statement \ref{BUOdd-HoTT} by $O$ and Statement
\ref{BURetract-HoTT} by $\neg R$, where $R$ refers to
$\prod\limits_{x : \SS^n} (-h(x) = h(-x))$. The first task in showing
the equivalence between $O$ and $\neg R$ is that
$O \Rightarrow \neg R $, or equivalently that $R \Rightarrow \neg
O$. To remind readers how this equivalence works in intuitionistic
logic, we have that
\[
  (O \Rightarrow \neg R)
  = (\neg O \lor \neg R)
  = (\neg R \lor \neg O)
  = (R \Rightarrow \neg O).
\]
With the logic settled, $R \Rightarrow \neg O$ follows from the same
argument as in the classical case. To be clear, $R$ assumes the
existence of an odd, continuous function
$h \from \SS^{n} \to \SS^{n-1}$. Let us recast this as a function
$h \from \SS^n \to \RR^n$ whose image lies in $\SS^{n-1}$, which
implies that $\prod\limits_{x \tin \SS^n} \neg (h(x)=0)$. This gives
us that $R \Rightarrow \neg O$.

The converse, $\neg R \Rightarrow O$, is equivalent to
$\neg O \Rightarrow \neg\neg R$. Because $R \Rightarrow \neg \neg R$,
it suffices to show that $\neg O \Rightarrow R$. By $\neg O$, we
assume the existence of an odd, continuous function
$g \from \SS^n \to \RR^n$ without any roots.  From this, define a new
function, $h(x) = g(x)/\vert g(x) \vert$ which is both odd and
continuous, plus has an image contained in $\SS^{n-1}$. Therefore, we
conclude $R$.

As mentioned above, we do not attempt to prove the above three
statements and instead prove versions involving truncations to make
them propositions, and involving the $\sharp$ modality to break the
continuous dependence of the bound variables on the free variables.  

\begin{statement}\label{BUClassic-RCHoTT}
  For any function $f \from \SS^n \to \RR^n$, we have
  $\int \vert\vert \sum\limits_{x \tin \SS^n} f(x) = f(-x) \vert\vert_0$.
\end{statement}

\begin{statement}\label{BUOdd-RCHoTT}
  For any odd continuous function $g: \SS^n \rightarrow \RR^n$, we
  have
  $\sharp \vert\vert\sum\limits_{x : \SS^n} (g(x) = 0) \vert\vert_0$.
\end{statement}

\begin{statement}\label{BURetract-RCHoTT}
  For any odd continuous function $h \from \SS^n \to \SS^{n-1}$, we
  have
  $\sharp \vert\vert neg \prod\limits_{x : \SS^n} -h(x) = h(-x)
  \vert\vert_0$.
\end{statement}

These equivalences follow from transporting the equivalences shown
above along the maps $(-)^\sharp \circ \vert\vert - \vert\vert$.  


% =================================================
% SECTION: DEFINING RPn
% =================================================
\section{Topological and homotopical real projective spaces}
\label{sec:rpn}

OUTLINE:
\begin{itemize}
\item
  Define n-disks as both sets and types, the latter which is
  simply 1, since they're contractible. Show that $ \shape
  \DD = \D $ 
\item
  Define n-spheres as sets.  Use pushouts to glue
  disks together. Explain why we need to glue with a
  collar---i.e. the ``topology'' (as encoded by continuous
  paths $ \RR \to \X $ of a type $ \X $. Show, via Shulman,
  that $ \shape \SS^n = \S^n $ 
\item
  Define $ \RRP^n $ as sets using pushouts and collaring.
  Recall Bulcholtz and Egbert's definition of HIT $ \RP^n
  $. \Chandrika{First draft done}
 \item
  Prove that $ \shape \set{RP}^n = \RP^n $, using an idea like "shape preserves pushouts".
\item
Show that the homology of $\set{RP}^n$ is what we want it to be (see Prop 5.1, in Amelia's section).
\end{itemize}

\subsection{Disks, Spheres and their shapes}
\subsection{Defining $\set{RP}^n$}
We define $\set{RP}^n$ using push outs, tautological bundles, spheres, and an inductive process, similar to the work of Rijike [].

The base case for our induction is $\set{RP}^1$.

\begin{definition}
We define $\set{RP}^1$ as the push out seen in the diagram below, where $\set{I}$ is the open unit interval, and the maps are defined by $a_1(-1,x) = \frac{x}{4}$ and $a_1(1,x)= \frac{x}{4} + \frac{3}{4}$, and $b_1 (\pm 1, x) := (0, a(\pm1, x))$.\\
\[\begin{tikzcd}
\set{S}^0 \times \set{I} \arrow[r, hook, "a_1"] \arrow[d, hook, "b_1" ] & \set{I} \arrow[d]\\
\{0 \} \times \set{I} \arrow[r] & \set{RP}^1
\end{tikzcd}
\]
\end{definition}

It is helpful to think of $a_1$ as an inclusion of a tubular neighbourhood of the boundary of $[0,1] \subseteq \set{R}$, with the boundary points deleted (so that it is indeed a subset of the open interval $\set{I}$). We call this a \emph{thickened boundary}. In fact, $b_1$ is also an inclusion of a thickened boundary. The image of $b_1$ is the deleted tubular neighbourhood of the boundary of $\{0\} \times [0,1] \subseteq \{0\} \times \set{R}$.

\begin{definition}
Let $A, B$ be two cohesive types, with $A$ an open subset of $B$. Let $\bar{A}$ be the closure of $A$ in $B$. Suppose $\bar{A}$ has a non-empty boundary, $\partial \bar{A}$. Let $N'$ be a neighbourhood of $\partial\bar{A}$ that is homotopy equivalent to $\partial\bar{A}$. Let $N := N' \setminus A^C$, where $A^C$ is the complement of $A$. Even though $A$ has no boundary, we call $N$ a \emph{thickened boundary of $A$, relative to $B$}.
 \end{definition}
%%% show that shape of \set{RP1} is S1.. start reading pg 63 of brouwer fixed pt paper.%%

We also need the following $\set{R}$-bundle as part of our base case. 
\begin{definition}(M\"{o}bius strip)
Let $\U_{\set{R}}$ be the universe of types homeomorphic to $\set{R}$. The \emph{tautological bundle of dimension one} $\mathcal{M}^1$, is an $\set{R}$ bundle over $\set{RP}^1$ defined by the map $m^1: \set{RP}^1 \rightarrow \U_{\set{R}}$, which is given by the constructors $\set{I} \mapsto \set{R}$, $\{0 \} \times \set{I} \mapsto \set{R}$, and the equivalence $\lambda x. x$ for every point in $\{0\} \times \set{I}$, and the equivalence $\lambda x. -x$ for every point in $\{1\} \times \set{I}$.
 \end{definition}

We would like to consider a thickened boundary of the M\"{o}bius strip $\mathcal{M}^1$. Our topological intuition is that if one were to thicken the boundary of a M\"{o}bius strip, they would get a thickened $\set{RP}^1$ (homeomorphic to a cylinder). However since $\mathcal{M}^1$ is not embedded in a larger space, a thickened boundary is not defined. To define the thickened boundary that we desire, note that the homeomorphism $\tau: \set{R} \rightarrow \set{I}$, defined by $\tau (x)=\text{arctan}(x)+ \frac{1}{2}$, can be used to define an embedding of $\mathcal{M}^1$ into a larger space as follows. We define $\tau(\mathcal{M}^1)$ as a $\set{I}$-bundle over $\set{RP}^1$, given by the composing the constructors of  $\mathcal{M}^1$ with $\tau$ (so that the codomain of the constructors is $\U_{\set{I}}$).  Note that there is a natural inclusion $\tau(\mathcal{M}^1) \hookrightarrow \mathcal{M}^1$ defined by $\lambda (x, y). (x,y)$ where $x: \set{RP}^1$ and $y : \set{I}$ (induced by the inclusion of $\set{I}$ into $\set{R}$ defined by $\lambda y. y$). At this point we have defined maps as follows.
\[
\mathcal{M}^1 \rightarrow \tau(\mathcal{M}^1) \hookrightarrow \mathcal{M}^1
\]
A thickened boundary of the inclusion of $\tau(\mathcal{M}^1)$ relative to $\mathcal{M}^1$ has a pre-image in $\tau(\mathcal{M}^1)$. Slightly abusing notation, we call this the thickened boundary of $\tau(\mathcal{M}^1)$. Now we consider the pre-image of this thickened boundary in $\mathcal{M}^1$. Continuing the slight abuse of notation, we call this pre-image the thickened boundary of $\mathcal{M}^1$. \Chandrika{Does  definition 4.3 up until here make sense? How can I prove that the thickened boundary of $\mathcal{M}^1$ is homeomorphic to $\set{S}^1 \times \set{I}$?}

From here, we proceed inductively with the definitions below. The definition of $\set{RP}^n$ depends on the definition of $\mathcal{M}^{n-1}$, which depends on $\set{RP}^{n-1}$, which depends on $\mathcal{M}^{n-2}$, and so on.

\begin{definition} $\set{RP}^n$ is defined (up to homeomorphism) as the following pushout.\\
\[\begin{tikzcd}
\set{S}^{n-1} \times \set{I} \arrow[r, hook, "a_n"] \arrow[d, hook, "b_n" ] &\set{D}^{n} \arrow[d]\\
\mathcal{M}^{n-1} \arrow[r] &\set{RP}^n\\
\end{tikzcd}
\] where $a_n$ and $b_n$ are both inclusions of $\set{S}^{n-1} \times \set{I} $ as thickened boundaries of $\mathcal{M}^{n-1}$ and $\set{D}^{n}$ (relative to $\set{R}^n$). The choice of thickened boundary does not change the homeomorphism type of $\set{RP}^n$.
\end{definition}
\Chandrika{Are others worried about only defining it up to homeomorphism? My thinking was that in type theory, things are only really ever defined up to equivalence, because of univalence.}
 

\begin{definition}
\label{defn:tautologicalbundle}
The tautological bundle $\mathcal{M}^n$ is defined by the map $m^n: \set{RP}^n \rightarrow \U_{\set{R}}$ which is given by the constructors $m^{n-1}$ (which defines $\mathcal{M}^{n-1}$), as well as $\set{D}^n \mapsto \set{R}$, together with the equivalence $\set{R}$, $\lambda x.x$ for every point of $\set{S}^{n-1} \times \set{I}$.
\end{definition}
\Chandrika{This should not be the trivial bundle because $\mathcal{M}^{n-1}$ is not trivial.}

%%%


\subsection{Showing $ \shape \set{RP}^n = \RP^n $}
Our first observation is that shape is a left adjoint operator, and so it preserves colimits. Therefore we have the following commutative diagram.
\[\begin{tikzcd}
\shape(\set{S}^{n-1} \times \set{I}) \arrow[r] \arrow[d] &\shape (\set{D}^{n}) \arrow[d]\\
\shape (\mathcal{M}^{n-1}) \arrow[r] &\shape (\set{RP}^n)\\
\end{tikzcd}
\] 

Based on work of Shulman \cite{shul:bfp}, we have $\shape(\set{S}^{n-1} \times \set{I}) =S^{n-1}$ and $\shape (\set{D}^{n})$ is the unit type. Next, we find $\shape (\mathcal{M}^{n-1})$ so that we may understand $ \shape \set{RP}^n$.  We begin by showing that $\mathcal{M}^{n}$ is a pushout for all $n$. Note that $\mathcal{M}^n= \sum _{x \in \set{RP}^n} m^n (x)$ where $m^n$ is the map taking each point in $\set{RP}^n$ to the fibre over it (see Definition~\ref{defn:tautologicalbundle}). Consider the following commutative diagram, where the bottom square in the cube is the pushout defining $\set{RP}^n$, and $m^n$ is the map defining the bundle  $ \mathcal{M}^{n}$ (in the top, front, right position in the cube). The maps $s$ and $q$ are induced by the pushout. The top square consists of bundles over each of the types in the bottom square with fibres are types homeomorphic to $\RR$. The map $\lambda$ above $s$ is defined by $\lambda (x,y). (s(x),y)$. The remaining maps in on the top square are similarly defined by each of the maps they lie over. \\
\begin{equation}
\begin{tikzcd}
																				& \sum_{x \in \set{S}^n \times \set{I}} m^n \circ s \circ b_n (x) \arrow[r]	\arrow[ld] \arrow[-, d, "p_4"] 	& \sum_{x \in \set{D}^n} m^n \circ q (x) \arrow[ld] \arrow[dd, "p_2"]\\
\sum_{x \in \mathcal{M}^{n-1}}  m^n \circ s (x) \arrow[r, crossing over, near start, "\lambda"] \arrow[dd, "p_3"]	& \sum_{x \in \set{RP}^n}m^n(x)\hspace{0.25cm} (=\mathcal{M}^n)	\arrow[d]								&	\\
																				& \set{S}^n \times \set{I} \arrow[r, "a_n"] \arrow[ld, "b_n"]										& \set{D}^n \arrow [ld, "q"]\\
\mathcal{M}^{n-1} \arrow[r, "s" ]															& \set{RP}^n \ar[rd, "m^n"] 																	& \\
																				&																						& \U_{\set{R}}\\
\arrow[from=2-2, to=4-2, crossing over, bend left = 60, "p_1"]
\end{tikzcd}
\label{cube}
\end{equation}

Pushouts are stable under pullback because all colimits are Van Kampen in $\infty$-toposes, which admits models for HoTT. Therefore, it suffices to show that the vertical faces of the cube are pullbacks in order to prove that the top face of the cube is a pushout. The vertical faces are pullbacks because composition with the classifying map $m^n$ yields a pullback of the total spaces. Therefore, the top face of the commutative diagram~(\ref{cube}) is a pushout.

\subsubsection{Showing that the front face of is a pullback}

\Chandrika{Do we feel safe to delete this?}
 We would like to show the following.
 \[
 \displaystyle\sum_{x \in \mathcal{M}^{n-1}} f\circ s (x) = \displaystyle\sum_{a \in \sum_{c \in \set{RP}^n}f(c)} \hspace {0.5cm}\displaystyle\sum_{b \in \mathcal{M}^{n-1}} (s(b) =p_1(a))
 \]
 
 In order to do this we define a homotopy equivalence between the left hand side and the right hand side. Let
 \[
 g:  \displaystyle\sum_{x \in \mathcal{M}^{n-1}} f\circ s (x) \longrightarrow \displaystyle\sum_{a \in \sum_{c \in \set{RP}^n}f(c)} \hspace {0.5cm}\displaystyle\sum_{b \in \mathcal{M}^{n-1}} (s(b) =p_1(a))
 \]
 be defined by $g (x, y) : = (\lambda(x, y), p_3(x, y), \text{refl}_{s\circ p_3(x,y)})$. Note that by the definition of $\lambda$, and the fact that $p_3$ is projection to the first coordinate, the right hand side simplifies to $((s(x), y), x, \text{refl}_{s(x)})$. This is in the codomain because the diagram commutes. Define
  \[
 h: \displaystyle\sum_{a \in \sum_{c \in \set{RP}^n}f(c)} \hspace {0.5cm}\displaystyle\sum_{b \in \mathcal{M}^{n-1}} (s(b) =p_1(a)) \longrightarrow  \displaystyle\sum_{x \in \mathcal{M}^{n-1}} f\circ s (x) 
 \]
by $h((c,r), b, k) := (b, r)$. The right hand side is a type in the codomain because $r : f(c)$, and $k$ is a witness that $(s(b)=c)$, so $r: f \circ s(b)$. Now we check that  $g\circ h$ and $h \circ g$ are homotopic to identity. Indeed,

\begin{align*}
g \circ h((c, r), b, k)	& = g(b, r) \\
				& = ((s(b), r), b, \text{refl}_{s(b)})\\
				& = ((c,r), b, \text{ref;}_{s(b)}),
\end{align*}
since $s(b) = c$ (as witnessed by $k$). It remains to show that $\text{refl}_{s(b)}=k$, but this must be true because $\set{RP}^n$ is a set. The simplification of $h \circ g$ is also straightforward.
\begin{align*}
h \circ g (x, y)	& = h((s(x), y), x, \text{refl}_{s(x)})\\
			& = (x, y),
\end{align*}
which is exactly what we wanted to show.  Therefore the front face of Diagram~\ref{cube} is a pullback.

The proof that the other faces of the cube in Diagram~\ref{cube} are pullbacks proceeds similarly. Therefore the top face (the face defining $\mathcal{M}^n$) is a pushout. 



\subsection{The $\mathbb{Z}$-homology of $\set{RP}^n$.}


% =================================================
% SECTION: COHOMOLGY
% =================================================
\section{Cohomology}
\label{sec:cohom}

OUTLINE:
\begin{itemize}
\item 
  \textbf{Subsection 1.} 
  Define cohomology for $ \ZZtwo $ coefficients and the
  EM-spaces for $ \RRP^n $ \Amelia{Done except for proof of prop 5.4}
\item
  \textbf{Subsection 2.} Show that we get a commutative
  graded ring structure for cohomology of any type $ \X $
  with $ \ZZtwo $-coefficients. Follow Brunerie's thesis.
\item
  \textbf{Subsection 3.} Compute $ \ZZtwo $-cohomology ring
  for $ \RRP^n $ using Mayer-Vietoris.  To do this we 
  first need to compute cohomology for disks and spheres.  
\end{itemize}


\subsection{Cohomology and EM-spaces for $\RRP^n$}


\Amelia{7/8/22: Based on convos in June, it seems like maybe we actually want $\RP^2$ in our cohomology not $\set{RP}^2$. is this accurate?}

We follow a similar construction for cohomology as found in \cite{brunerie:thesis}, modifying their construction with $\ZZ$ coefficients to have coefficients in $\ZZtwo$. In order to define cohomology, we must first define Eilenberg-MacLane spaces $\KZtwo{n}$. We follow the definition for Eilenberg-MacLane spaces $K(G,n)$ for arbitrary group $G$ given by Finster and Licata in \cite{fl:em}, although we omit the final truncation at level $n$, since our .

We give a construction of $\RRP^n$ in Section \ref{sec:rpn}, which shows that $\trunc{\RRP^2}_1$ will have the homotopy groups necessary to be the foundation of our Eilenberg-MacLane spaces. 
\begin{proposition}\label{prop:rpnhtpygps} %update this label when sec:rpn is done
	\[ \pi_n(\trunc{\RRP^2}_1)=\left\{ \begin{array}{ll} 0 & \text{for }n=0\\
	\ZZtwo & \text{for } n=1\\
	0 & \text{for } n> 1, 
	\end{array}\right.\]
\end{proposition}
\begin{proof}
	\Amelia{7/8/22: Again, need to check proof logic for which $RP$ to use.}
\end{proof}

\begin{definition}\label{def:EM-space}
	For $n:\NN$, the type \defn{Eilenberg-MacLane space} $\KZtwo{n}$ is the $n$-truncated and $(n-1)$-connected pointed type defined by
	\[ \KZtwo{n}:=\left\{ \begin{array}{ll} \ZZtwo & \text{for }n=0\\
	\trunc{\Sigma^{n-1}\trunc{\RRP^2}_1}_n & \text{for } n\ge 1, 
	\end{array}\right.\]
	where $\Sigma^{n-1}$ indicates the reduced suspension $n-1$ times. 
\end{definition}

\begin{proposition}
	This definition of $\KZtwo{n}$ does indeed define an Eilenberg-MacLane Space. 
\end{proposition}

\begin{proof} This follows from Prop \ref{prop:rpnhtpygps} and
	\Amelia{the fact (that I don't have a HoTT reference for) that EM spaces are unique.}
\end{proof}


\Amelia{On October 17 2019 we talked about this question of what results port over. we said: According to Mike, in classic topology, EM spaces are unique up to unique isomorphism, however in HoTT they are equivalent up to homotopy but the homotopy may not be unique. Our thought was that our K(G,1) should be homotopy equivalent to theirs, so by univalence they're equal as types. So, their results for their construction of K(G,1) should apply to ours.  }

As noted in \cite{fl:em}, Eilenberg-MacLane spaces have the following delooping property. This property allows us to construct a spectrum for ordinary cohomology with $\ZZtwo$ coefficients. 

\begin{proposition}\label{prop:EM-loop-equiv}
	\[K(\ZZtwo,n)\simeq \Omega K(\ZZtwo,n+1)\]
	\end{proposition}
\Amelia{ 6/24/22: come back and fill in this proof later. It should be an easy connectivity argument about}

Given this construction of the Eilenberg-MacLane spaces, we define cohomology in the following way. 

\begin{definition}
	For a type $\X$ and $n:\NN$, the \defn{$n$-th cohomology group of $\X$ with coefficients in $\ZZtwo$} is the type
	\[H^n(\X;\ZZtwo):= \trunc{\X\rightarrow \KZtwo{n}}_0.\] 
\end{definition}
\Amelia{B also defines reduced cohomology as well. I'm not sure we need that. G proved a reduced MV sequence, so we may need it if we also use MV. Leaving it out for now.}



\subsection{Commutative Graded Ring Structure}

For a ring $R$, the multiplication operation on $R$ can be viewed as a homomorphism $R\otimes R\to R$, where $R\otimes R$ is the tensor product of the underlying abelian groups. Our strategy for describing the graded ring structure is to show that $||K(R,n)\wedge K(R,m)||_{n+m} = K(R\otimes R, n+m)$, then  lift the ring multiplication of $R \otimes R \to R$ to a cup product on cohomology with $R$-coefficients.


\Amelia{3/8/22: Probably shouldn't go into more detail on this tensor in the finished write up, but for my own sanity: For abelian groups $G$ and $H$, $G\otimes H$ is the quotient $G\times H/\sim$ where \begin{itemize}
		\item $(g_1,h)+(g_2,h)\sim (g_1+g_2,h)$
		\item $(g,h_1)+(g,h_2)\sim (g,h_1+h_2)$.
	\end{itemize}
So if we define $\cdot:R\otimes R\to R$ by $\cdot(a,b)=ab$, then the distributive axiom of rings and bilinearity of tensor gives us a group homomorphism because:
\[\cdot((a_1,b)+(a_2,b))=\cdot(a_1+a_2,b)=(a_1+a_2)b=a_1b+a_2b=\cdot(a_1,b)+\cdot(a_2,b)\]
}

\begin{proposition}\label{prop:K_smash}
	$ \trunc{K(R,n) \wedge K(R,m)}_{n+m} = K(R \otimes R, n+m)$ for $n,m\geq 1$.
\end{proposition} 


\begin{proof}
	Recall that $K(R \otimes R, n+m)$ is the unique up to homotopy space
	having the property that
	\[
	\pi_k (K(R \otimes R, n+m )) \cong
	\begin{cases}
	0, & k \neq n+m \\
	R \otimes R, & k= n+m \\
	\end{cases}
	.\]
	
	
	Thus, by showing that $ || K(R,n) \wedge K(R,m) ||_{n+m} $
	satisfies this property, we have the desired
	equivalence. 
	
	In order to establish the property for $k=n+m$, it is a known result (see \cite[Prop 19.60]{strom:mcht}) that for $n,m\geq 1$
	\[
	\pi_{n+m} ( || K(R,n) \wedge K(R,m) ||_{n+m} )
	\cong R \otimes R.
	\]
	
	In the case where $k>m+n$, 
	 $ || K(R,n) \wedge K(R,m) ||_{n+m} $
	is truncated to be an $ ( n+m ) $-type. So, \[
	\pi_k ( || K(R,n) \wedge K(R,m) ||_{n+m} )
	\cong 0,
	\] for $k>n+m$. 
	
	Finally, note that  
	$ || K(R,n) \wedge K(R,m) ||_{n+m} $ is
	$ ( n+m-1 ) $-connected, which follows from $ K( R,k ) $ being
	$ ( k-1 ) $-connected, as seen in \cite[Prop 4.3.1]{brunerie:thesis}.
	Thus,
	\[
	\pi_k (|| K(R,n) \wedge K(R,m) ||_{n+m} ) \cong 0
	\]
	for $ k \leq n+m-1 $.
	
	We have shown the desired property and arrive at the homotopy equivalence 
	\[
	|| K(R,n) \wedge K(R,m) ||_{n+m} \simeq
	K (R \otimes R, n+m ).
	\]
	Invoking the univalence axiom, we conclude that
	\[
	|| K(R,n) \wedge K(R,m) ||_{n+m} =
	K (R \otimes R, n+m ).
	\]
\end{proof}



Next, we construct the ring structure on cohomology. The
strategy is to define the necessary structures and properties on Eilenberg-MacLane spaces (Def. \ref{def:EM-space})
and then lift those to cohomology.



The addition and additive inverse
operations follow
directly from \cite{brunerie:thesis}, and satisfy the properties to make $K(\ZZtwo,n)$ an abelian group. When $n=0$, addition and additive inverses are defined as usual in $\ZZtwo$. For $n>0$, addition and additive inverses are defined via the equivalence $\KZtwo{n}\simeq \Omega\KZtwo{n+1}$ using the composition and inverse of loops respectively. We restate the operation properties below.


\begin{proposition}\cite[Prop. 5.1.4]{brunerie:thesis}\label{prop:abeliangpops}
	The maps $ +: K(\ZZtwo,n) \times K(\ZZtwo,n) \to K(\ZZtwo,n) $ and $-: K(\ZZtwo,n)  \to K(\ZZtwo,n) $ have the following properties for all $n:\NN$ and $x$, $y$, $z:K(\ZZtwo,n)$:
	
	\[x+0=x,\]
	\[0+x=x,\]
	\[x+(-x)=0,\]
	\[(-x)+x=0,\]
	\[(x+y)+z=x+(y+z),\]
	and
	\[x+y=y+x.\]
	
	\end{proposition}



We now define the ring multiplication operation. From the multiplication
$ \ZZtwo \otimes \ZZtwo \to \ZZtwo $, we induce a multiplication
$ K(\ZZtwo \otimes \ZZtwo, n)\to K(\ZZtwo, n) $ by applying the
functor
\[
K(-,n) \from \mathbf{Ring} \to \mathbf{Ho}(\mathbf{Top_\ast}).
\]
\Amelia{Do we know that $K(-,n)$ is a functor in HoTT? It is a functor, but I'm not sure we ever proved it and I don't think it's explicitly stated in Finster-Licata. I'm not sure what it does to morphisms, which I need to prove things about cohomology.}

As we showed in Proposition \ref{prop:K_smash}, 
\[
|| K(R,n) \wedge K(R,m) ||_{n+m} =
K (R \otimes R, n+m )
\]
for any ring $ R $, and so we can treat our multiplication as
\[
\widehat{\mu} \from
|| K(\ZZtwo,n) \wedge K(\ZZtwo,m) ||_{n+m} \to K(\ZZtwo, n+m).
\]


However, we want the domain of multiplication
to be $ K ( \ZZtwo , n) \times K( \ZZtwo, m) $, without the truncation. To get this, we
precompose $ \widehat{\mu} $ by several canonical arrows
resulting in the composite
\[
K (\ZZtwo , n) \times K(\ZZtwo, m)
\xrightarrow{\type{proj}}
K (\ZZtwo , n) \wedge K(\ZZtwo, m)
\xrightarrow{|-|_{n+m}}\cdots\]
\[\rightarrow|| K (\ZZtwo , n) \wedge K(\ZZtwo, m) ||_{n+m}
\xrightarrow{\widehat{\mu}}
K(\ZZtwo, n+m)
\]
that we call \emph{multiplication} $ \mu $. The proceeding definition only works when $n,m\geq 1$. In the special case where $n$ or $m$ is 0, we use the fact that $\KZtwo{0}=\ZZtwo$ and we define $\mu$ as one would expect: $\mu(x,0)=\mu(0,x)=0$ and $\mu(x,1)=\mu(1,x)=x$. 

\Amelia{July 2022: I'm trying a slightly different approach to defining $\widehat{\mu}$ but I need some help. This assumes that our idea in June that we should actually be using $\RP^2$ rather than $\set{RP}^2$ in the definition of cohomology. If that's incorrect, then throw out everything between the red asterisks.\\ 
	**********
}

We need to define $\widehat{\mu}:\trunc{K_n\wedge K_m}_{n+m}\to K_{n+m}$. When $n$ or $m$ is zero, this is done, so assume $n,m\geq 1$. 

So, we need a map
\[\trunc{\trunc{\Sigma^{m-1}\trunc{\RP^2}_1}_m\wedge\trunc{\Sigma^{n-1}\trunc{\RP^2}_1}_n}_{n+m}\to\trunc{\Sigma^{n+m-1}\trunc{\RP^2}_1}_{n+m},\]
which we could induce by a map (dropping the outer $n+m$ truncations)
\[\trunc{\Sigma^{m-1}\trunc{\RP^2}_1}_m\wedge\trunc{\Sigma^{n-1}\trunc{\RP^2}_1}_n\to\Sigma^{n+m-1}\trunc{\RP^2}_1,\]
\Amelia{Which I am hoping (need to come back again and think through if this is legal) we can drop the $m$ and $n$ truncations from and induce the above map from:}

\[\Sigma^{m-1}\trunc{\RP^2}_1\wedge\Sigma^{n-1}\trunc{\RP^2}_1\to\Sigma^{n+m-1}\trunc{\RP^2}_1.\]

Since suspension is equivalent to smashing with $S^1$,

\[\Sigma^{m-1}\trunc{\RP^2}_1\wedge\Sigma^{n-1}\trunc{\RP^2}_1\simeq \left(S^1\wedge\right)^{\times m-1}\trunc{\RP^2}_1\wedge\left(S^1\wedge\right)^{\times n-1}\trunc{\RP^2}_1\]
\[\simeq\Sigma^{n+m-2}\trunc{\RP^2}_1\wedge\trunc{\RP^2}_1.\]
So, $\widehat{\mu}$ would be induced by
\[\trunc{\RP^2}_1\wedge \trunc{\RP^2}_1\to \Sigma\trunc{\RP^2}_1.\]





\Amelia{**********}

We will use this multiplication $\mu$ to induce
the cup product
\[
\smile \from H^n(X) \times H^m(X) \to H^{n+m}(X)
\]
on cohomology. 



Recall that we define the $ n $-th cohomology
with $ \ZZtwo $-coefficients to be
$H^n(\X;\ZZtwo)= \trunc{\X\rightarrow \KZtwo{n}}_0$. This is the
standard definition in homotopy type theory, rather than
singular cochains, because using singular cochains is not
a continuous process. 

Define
$ \smile ( |\alpha|, |\beta|)  $, for
$ \alpha \from X \to_\ast \KZtwo{n} $ and
$ \beta \from X \to \KZtwo{m} $, to be the truncation of the
pairing $ \langle \alpha, \beta \rangle $ followed by $ \mu $:
\[
\smile ( |\alpha|, |\beta|)  :
|| X \to \KZtwo{n} \times \KZtwo{m} \to \KZtwo{n+m} ||_0.
\]
Thus $ \smile ( |\alpha|, |\beta| ) $ type-checks. It
remains to show the usual ring properties hold for $ H^n(X)
$.  

We prove the distributive property similarly to Proposition 5.1.8 in \cite{brunerie:thesis}.
\begin{proposition}
	The multiplication map \[{\mu}:\KZtwo{n}\times\KZtwo{m}\to \KZtwo{n+m}\] distributes over addition.
	\end{proposition}

\begin{proof} We abbreviate $\KZtwo{i}$ by $K_i$ to save space. Let $a:K_n$ and $b,c:K_m$. We must show that $\mu(a,b+c)=\mu(a,b)+\mu(a,c)$. 
	
	First, consider the case where $m=0$. Since $K_0=\ZZtwo$, $b$ and $c$ are each either 0 or 1. Note that since $\mu$ is induced by the multiplication map $\ZZtwo\otimes\ZZtwo\to\ZZtwo$, $\mu(x,0)=\mu(0,x)=0$. So, if $b=0$, it follows from the properties in Proposition \ref{prop:abeliangpops} that \[\mu(a,b+c)=\mu(a,0+c)=\mu(a,c)=\mu(a,0)+\mu(a,c)=\mu(a,b)+\mu(a,c).\]
	Distributivity holds similarly in the case where $c=0$. If $b=c=1$, then
	\[\mu(a,b)+\mu(a,c)=\mu(a,1)+\mu(a,1)=a+a,\]
	which equals 0 because composing a loop with itself in $\RRP^2$ results in a trivial loop. Thus when $m=0$, $\mu$ distributes over addition.
	
	Now consider $m>0$. We prove distributivity by showing there is a filler of the following diagram.
	
	\[\begin{tikzcd}
	K_n\wedge\left(K_m\times K_m\right) \arrow[rr,"id\wedge+"] \arrow[d,"p"]&  & K_n\wedge K_m\arrow[d,"\widehat{\mu}"]\\
	\left(K_n\wedge K_m\right)\times\left(K_n\wedge K_m\right)\arrow[r,"\widehat{\mu}\times\widehat{\mu}"] & K_{n+m}\times K_{n+m}\arrow[r,"+"] &K_{n+m}	
	\end{tikzcd}\]
	The map $p$ on the left sends $\type{proj}(a,(b,c))$ to $(\type{proj}(a,b),\type{proj}(a,c))$. 
	
	\Amelia{3/22/22: Leaning on G's thesis this much seems like lazy writing... but I also didn't want to just re-write a bunch of bits from his thesis. This is coming from the proof of prop 4.3.1 and prop 3.2.8(which has multiple steps)}
	
	As shown in Propositions 4.3.1 and 3.2.8 of \cite{brunerie:thesis}, if $A$ and $B$ are two pointed types such that $A$ is $r$-connected and $B$ is $s$-connected, then map $i:A\vee B\to A\times B$ is $(r+s)$-connected. Since $K_{m}$ is $(m-1)$-connected, $i:K_{m}\vee K_{m}\to\KZtwo{m}\times K_{m}$ is $(2m-2)$-connected. Then the map 
	\[f:K_{n}\wedge\left(K_{m}\vee K_{m}\right)\to K_{m}\wedge\left(K_{m}\times K_{m}\right)\]
	given by 
	\[f(\type{proj}(a,\type{inl}(b))):=\type{proj}(a,(b,0))\text{~and~} f(\type{proj}(a,\type{inr}(c))):=\type{proj}(a,(0,c))\]
	is $(n+2m-2)$-connected. Since $m\geq 1$, $n+2m-2\geq n+m+1$. Since $K_{n+m}$ is $(n+m)$-truncated...
	\Amelia{4/26/22: Something is not clicking for me here. I See that $K_{n+m}$ is $n+m$ truncated. Some how that combined with $f$ being connected to at least that degree means we can just consider elements in the image of $f$ and show those commute. but I don't see why at the moment.  }
	
	Elements in the image of $f$ look like either $\type{proj}(a,(b,0))$ or $\type{proj}(a,(0,c))$. By Proposition \ref{prop:abeliangpops}, $b+0=0$ and $0+c=0$. \Amelia{4/26/22: but i'm not clear enough on our multiplication map to say that $a\cup 0 =0$}
	

	
	\end{proof}



 To show
`graded commutativity', it suffices to show standard
commutativity because of the $ \ZZtwo $-coefficients.  
\Amelia{(3/15/22) need to add a prop showing commutativity}




\subsection{Computing the Cohomology Ring of $\RRP^n$}




% =================================================
% SECTION: PROVING THE BORSUK ULAM THEORM
% =================================================
\section{The Borsuk-Ulam theorem}
\label{sec:borsuk-ulam}

OUTLINE:
\begin{itemize}
\item
  The proof is done by this point. Just put it all
  together and reconnect the dots for the reader.
\end{itemize}


% =================================================
% BIBLIOGRAPHY
% =================================================
\bibliographystyle{alpha}
\nocite{shul:bfp,brunerie:thesis,br:rp-hott}
\bibliography{assets/appcoh}


\end{document}